Competing Bandits: The Perils of Exploration under Competition

### 2018-09-03 paper/content/inverted_u.tex
cosmetic changes

% latex table generated in R 3.4.0 by xtable 1.8-2 package
% Thu Aug 16 13:13:01 2018
\begin{table}[ht]
\centering
\caption{Duopoly experiment for heavy tail instances}
\begin{tabular}{|c|c|c|c|}
  \hline
 & $T_0$ = 20 & $T_0$ = 250 & $T_0$ = 500 \\ 
  \hline
TS vs DG & \makecell{\textbf{0.29} $\pm$0.03\\ eeog \\ avg: 55\\ med: 0} & \makecell{\textbf{0.72} $\pm$0.02\\ eeog \\ avg: 570\\ med: 0} & \makecell{\textbf{0.76} $\pm$0.02\\ eeog \\ avg: 620\\ med: 98.5} \\ 
\hline  
  TS vs DEG & \makecell{\textbf{0.3} $\pm$0.03\\ eeog \\ avg: 37\\ med: 0} & \makecell{\textbf{0.88} $\pm$0.01\\ eeog \\ avg: 480\\ med: 0} & \makecell{\textbf{0.9} $\pm$0.01\\ eeog \\ avg: 570\\ med: 113.5} \\ 
\hline  
  DG vs DEG & \makecell{\textbf{0.62} $\pm$0.03\\ eeog \\ avg: 410\\ med: 7} & \makecell{\textbf{0.6} $\pm$0.02\\ eeog \\ avg: 790\\ med: 762} & \makecell{\textbf{0.57} $\pm$0.03\\ eeog \\ avg: 730\\ med: 608} \\ 
   \hline
\end{tabular}
\label{sim_ht}
\end{table}

\begin{table}[ht]
\centering
\caption{Duopoly experiment for needle in haystack instances}
\begin{tabular}{|c|c|c|c|}
  \hline
 & $T_0$ = 20 & $T_0$ = 250 & $T_0$ = 500 \\
  \hline
TS vs DG & \makecell{\textbf{0.64} $\pm$0.03\\ eeog \\ avg: 200\\ med: 27} & \makecell{\textbf{0.6} $\pm$0.03\\ eeog \\ avg: 370\\ med: 0} & \makecell{\textbf{0.64} $\pm$0.03\\ eeog \\ avg: 580\\ med: 121.5} \\
\hline  
  TS vs DEG & \makecell{\textbf{0.57} $\pm$0.03\\ eeog \\ avg: 150\\ med: 14} & \makecell{\textbf{0.52} $\pm$0.03\\ eeog \\ avg: 460\\ med: 78.5} & \makecell{\textbf{0.56} $\pm$0.02\\ eeog \\ avg: 740\\ med: 627.5} \\
  \hline
  DG vs DEG & \makecell{\textbf{0.46} $\pm$0.03\\ eeog \\ avg: 340\\ med: 128.5} & \makecell{\textbf{0.42} $\pm$0.02\\ eeog \\ avg: 650\\ med: 408} & \makecell{\textbf{0.42} $\pm$0.02\\ eeog \\ avg: 690\\ med: 466.5} \\
   \hline
\end{tabular}
\label{sim_nih}
\caption*{{The first line in each cell contains the average market share received by the firm playing Alg 1 (and the market share of Alg 2 is 1 - Alg 1 Market Share) as well as a 95\% confidence band. For example, the cell in the top left indicates that TS gets on average 64\% of the market when played against DG. The next line contain the average and median effective end of game for this set of simulations.}}
\end{table}
% latex table generated in R 3.4.0 by xtable 1.8-2 package
% Thu Aug 16 13:13:00 2018

>>>>

% latex table generated in R 3.4.0 by xtable 1.8-2 package
% Thu Aug 16 13:13:01 2018
\begin{table}[ht]
\centering
\caption{Duopoly experiment for heavy tail instances}
\begin{tabular}{|c|c|c|c|}
  \hline
 & $T_0$ = 20 & $T_0$ = 250 & $T_0$ = 500 \\ 
  \hline
$\TS$ vs $\DG$ & \makecell{\textbf{0.29} $\pm$0.03\\ eeog \\ avg: 55\\ med: 0} & \makecell{\textbf{0.72} $\pm$0.02\\ eeog \\ avg: 570\\ med: 0} & \makecell{\textbf{0.76} $\pm$0.02\\ eeog \\ avg: 620\\ med: 98.5} \\ 
\hline  
  $\TS$ vs $\DEG$ & \makecell{\textbf{0.3} $\pm$0.03\\ eeog \\ avg: 37\\ med: 0} & \makecell{\textbf{0.88} $\pm$0.01\\ eeog \\ avg: 480\\ med: 0} & \makecell{\textbf{0.9} $\pm$0.01\\ eeog \\ avg: 570\\ med: 113.5} \\ 
\hline  
  $\DG$ vs $\DEG$ & \makecell{\textbf{0.62} $\pm$0.03\\ eeog \\ avg: 410\\ med: 7} & \makecell{\textbf{0.6} $\pm$0.02\\ eeog \\ avg: 790\\ med: 762} & \makecell{\textbf{0.57} $\pm$0.03\\ eeog \\ avg: 730\\ med: 608} \\ 
   \hline
\end{tabular}
\label{sim_ht}
\end{table}

\begin{table}[ht]
\centering
\caption{Duopoly experiment for needle in haystack instances}
\begin{tabular}{|c|c|c|c|}
  \hline
 & $T_0$ = 20 & $T_0$ = 250 & $T_0$ = 500 \\
  \hline
$\TS$ vs $\DG$ & \makecell{\textbf{0.64} $\pm$0.03\\ eeog \\ avg: 200\\ med: 27} & \makecell{\textbf{0.6} $\pm$0.03\\ eeog \\ avg: 370\\ med: 0} & \makecell{\textbf{0.64} $\pm$0.03\\ eeog \\ avg: 580\\ med: 121.5} \\
\hline  
  $\TS$ vs $\DEG$ & \makecell{\textbf{0.57} $\pm$0.03\\ eeog \\ avg: 150\\ med: 14} & \makecell{\textbf{0.52} $\pm$0.03\\ eeog \\ avg: 460\\ med: 78.5} & \makecell{\textbf{0.56} $\pm$0.02\\ eeog \\ avg: 740\\ med: 627.5} \\
  \hline
  $\DG$ vs $\DEG$ & \makecell{\textbf{0.46} $\pm$0.03\\ eeog \\ avg: 340\\ med: 128.5} & \makecell{\textbf{0.42} $\pm$0.02\\ eeog \\ avg: 650\\ med: 408} & \makecell{\textbf{0.42} $\pm$0.02\\ eeog \\ avg: 690\\ med: 466.5} \\
   \hline
\end{tabular}
\label{sim_nih}
\caption*{{The first line in each cell contains the average market share received by the firm playing Alg 1 (and the market share of Alg 2 is 1 - Alg 1 Market Share) as well as a 95\% confidence band. For example, the cell in the top left indicates that TS gets on average 64\% of the market when played against DG. The next line contain the average and median effective end of game for this set of simulations.}}
\end{table}
% latex table generated in R 3.4.0 by xtable 1.8-2 package
% Thu Aug 16 13:13:00 2018
